{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to Near-Infrared Spectroscopy}

### 2022-01-28 Paper/main.tex
Paper work
3.2
Moved basis plots to appendix; added equation

	\begin{equation}
		\int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

@@

	Therefore, its basis functions inherits a repeating behaviour which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$. Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthogonal when the values $t_j$ are equally spaced within $T$. This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.  
	\begin{figure}[H]\label{fourier_basis}
	\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
	\caption{Fourier basis functions for $i = 1,\dots,6$}
	\end{figure}

@@

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[ c_j \sum_{k \in \mathcal{L}} \textcolor{teal}{d_k(\omega) \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
			= \alpha + \sum_{j \in \mathcal{I}} \left[c_j \sum_{k \in \mathcal{L}}  \textcolor{teal}{Z_{j, k}(\omega)} \right] + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}(\omega)} \right] + \epsilon(\omega)
			= \alpha + \sum_{j = 1}^{J} \left[c_j \textcolor{violet}{\tilde{Z}_{j}^{K}(\omega)} \right] + \epsilon(\omega)	
		\end{split}
	\end{equation}

@@

>>>>

	\begin{equation}
		{\color{orange} \lvert \lvert f \rvert \rvert^2 =} \int_{0}^{1} \lvert f \rvert^2 \mathrm{d}\mu < \infty
	\end{equation}

@@

	Therefore, its basis functions inherits a repeating behaviour which is useful to expand functions that represent an periodic or seasonal underlying process over the period $T$. Rephrasing from \cite{ramsay_functional_2005}, the Fourier basis functions are orthogonal when the values $t_j$ are equally spaced within $T$. This basis is suitable to expand functions with a similar curvature order across the domain, resulting generally in uniformly smooth expansions.

@@

	\begin{equation}\label{basis_exp_transf}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j \in \mathcal{I}} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k \in \mathcal{L}} d_k(\omega)  \psi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j \in \mathcal{I}} \left[ c_j d_k(\omega)\sum_{k \in \mathcal{L}} \textcolor{teal}{ \int_{0}^{1} \phi_j(s) \psi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
			= \alpha + \sum_{j \in \mathcal{I}} \left[c_j d_k(\omega) \sum_{k \in \mathcal{L}}  \textcolor{teal}{Z_{j, k}} \right] + \epsilon(\omega) \\
			& \approx \alpha + \sum_{j = 1}^{J} \left[c_j d_k(\omega) \textcolor{violet}{\sum_{k = 1}^{K}  Z_{j, k}} \right] + \epsilon(\omega)
			= \alpha + \sum_{j = 1}^{J} \left[c_j d_k(\omega)\textcolor{violet}{\tilde{Z}_{j}^{K}} \right] + \epsilon(\omega)	
		\end{split}
	\end{equation}

	A typical choice in this scenario is to use the same functional basis and the same truncation parameter for both the coefficient function and the approximation of the observations. This leads to the following simplification of Equation \ref{basis_exp_transf}.

	\begin{equation}
		\begin{split}
			Y(\omega) & = \alpha + \int_{0}^{1} {\color{blue}\beta(s)} {\color{red}X(\omega)(s)}\mathrm{d}s + \epsilon(\omega) \\
			& \approx \alpha + \int_{0}^{1}\left[{\color{blue}\left(\sum_{j = 1}^{L} c_j  \phi_j(s)\right)} {\color{red}\left(\sum_{k  = 1}^{L} d_k(\omega)  \phi_k(s)\right)} \right]\mathrm{d}s + \epsilon(\omega) \\
			& = \alpha + \sum_{j = 1}^{L} \left[\sum_{k = 1}^{L} c_j d_k(\omega) \textcolor{teal}{ \int_{0}^{1} \phi_j(s) 	\phi_k(s) \mathrm{d}s}\right] + \epsilon(\omega)
			= \alpha + \sum_{j = 1}^{L} \sum_{k = 1}^{L}  c_j d_k(\omega)\textcolor{teal}{Z_{j, k}}  + 	\epsilon(\omega)	
		\end{split}
	\end{equation}

@@

	\subsection{Basis Plots}

	\begin{figure}[H]\label{fourier_basis}
		\includegraphics[width = \textwidth]{../Graphics/Fourier_Basis.pdf}
		\caption{Fourier basis functions for $i = 1,\dots,6$}
	\end{figure}
